Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-06-30 talk/dls2012/paper.tex
work on slides a bit

>>>>

A dynamically typed language needs to do a lot of type
checking and unwrapping. For tight computationally intensive loops a
significant amount of the execution time might be spend on such tasks
instead of the actual calculations. Moreover, the type checking and
unwrapping is often loop invariant and performance could be increased
by moving those operations out of the loop. We propose to design a
loop-aware tracing JIT to perform such optimization at run time.
